\vspace{-0.25em}\thetitle

### 2009-07-16 paper.tex
Special formatting instructions for Infocom 2010.
...

\documentclass[conference]{IEEEtran}

@@

>>>>

\documentclass[conference]{IEEEtran}
\makeatletter
\def\ps@headings{%
\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
\def\@oddfoot{}%
\def\@evenfoot{}}
\makeatother
\pagestyle{headings}

@@

\newfootnote{\flownote}{We use the common definition of a \textit{flow} as a sequence of packets sharing the same  ``5-tuple'': \caps{IP} protocol type, source and destination nodes, and \caps{TCP/UDP} port numbers.}

This paper is the first in a three-part series, employing non-parametric discrete mixture modeling to understand and analyze network traffic patterns at the level of individual flows and packets.\flownote
All three papers employ the same theoretical framework but apply it to different aspects of network traffic analysis: prediction, classification and generation.
In this paper we present the framework and demonstrate how to predict detailed behavior of individual flows from the observation of only a handful of initial packets.
% The following papers will focus on classification of flows according to application type and realistic workload generation.

The fundamental concept underlying this work is that of a \emph{linear representation of network traffic}~\cite{Karpinski08}.
Linear representations operate on traffic traces at the level of flows.
A representation is a function that maps sets of flows to points in a vector space;
the space will typically have high dimension, each coordinate describing some aspect of flow behavior.
The representation must satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
The complete behavior of a traffic trace is expressed as a matrix, where each flow in the trace is represented by a row of the matrix.

% Karpinski~\emph{et~al.}~\cite{Karpinski08} further observed that the simplifications commonly used in traffic modeling correspond to multiplication of traffic representation matrices by low-rank matrices, averaging over rows or columns.
% They demonstrated experimentally that such simplifications severely distort important behavioral properties of traffic traces;
% viewing these simplification as low-rank matrix transformations, this is unsurprising:
% most of the detail of the original traffic behavior is destroyed.
% It was suggested that matrix factorization provides an alternative and superior means of model reduction.

The key observation of this work is that even real network traces tend to have approximately low-rank representation matrices.
